### 2017-11-15 Risk analysis/Text/Layout/Layout/chapter3_results.tex
Auto stash before merge of "master" and "origin/master"

		Regarding the different mechanisms of maximum trap volume control, it can be observed (see Figure \ref{fig:ML1} (c)) that all four relevant mechanisms occurred. The dominant factor is the anticlinal spill point (labeled "SPILL POINT"), accounting for more than 60\% of model realizations. It is followed by cross-fault leakage due to juxtaposition with formations underlying ("LEAK UNDER", ~20\%) and formations overlying ("LEAK OVER", ~13\%) the seal in the footwall. Leakage due to stratigraphical connections to seal-overlying units ("STRAT"), i.e. stratigraphical breaches of the seal, were registered to be decisive in only about 3\% of realizations. A satisfactory reliability of model algorithms and computation is indicated by the lack of unrecognized mechanisms (labeled "UNCLEAR", see Figure \ref{fig:ML1} (c)).\\

@@

		\subsection{Posterior model I}
		\begin{table}[h]
			\centering
			\begin{tabular}{lrr} 
				\toprule
				Model I - Likelihoods: layer thicknesses (normal distributions)\\  
				\midrule 
				Formation & $\mu$ [m] & $\sigma$ [m]\\ 
				\midrule 
				Sandstone 2 & 150 & 30 \\
				Shale (Seal) & 350 & 30\\ 
				Sandstone 1 (Reservoir) & 250 & 30 \\
				\bottomrule
			\end{tabular}
			\caption{Layer thickness likelihoods determined by normal distributions as used for posterior model I.}
			\label{tab:ML1_likelihoods}
		\end{table}
		For the simulation of this first posterior model, thickness likelihoods for the three central layers were defined (see Table \ref{tab:ML1_likelihoods}).
		\begin{figure}[p!]
			\centering
			\includegraphics[width=1\textwidth]{Figures/ML1}
			\caption{....}\label{fig:ML1}
		\end{figure}

		\subsection{Posterior model II}%ML3
		-results similar to I, basically same
		- results of ML1 generally similar as for ML3:
		i.e. thicker reservoir does not mean higher volume, as we didn't implement a direct uncertainty to the shape, the spill point will stay more or less the same
		-> spill and leak point as limiting factors to max volume
		-> max volume already defined in prior (ROV max 5,500,000)

		\subsection{Posterior model III}%ML2
		\begin{figure}[p!]
			\centering
			\includegraphics[width=1\textwidth]{Figures/ML2}
			\caption{....}\label{fig:ML2}
		\end{figure}
		- see ML2: seal thickness as decisive factor
			-> if seal thin and reservoir thick see the ratio of both!), higher likelihood of surpassing SSF

>>>>

		Regarding the different mechanisms of maximum trap volume control, it can be observed (see Figure \ref{fig:ML1} (c)) that all four relevant mechanisms occurred. The dominant factor is the anticlinal spill point (labeled "SPILL POINT"), accounting for more than 60\% of model realizations. It is followed by cross-fault leakage due to juxtaposition with formations underlying ("LEAK UNDER", ~20\%) and formations overlying ("LEAK OVER", ~13\%) the seal in the hanging wall. Leakage due to stratigraphical connections to seal-overlying units ("STRAT"), i.e. stratigraphical breaches of the seal, were registered to be decisive in only about 3\% of realizations. A satisfactory reliability of model algorithms and computation is indicated by the lack of unrecognized mechanisms (labeled "UNCLEAR", see Figure \ref{fig:ML1} (c)).\\

@@

		\subsection{Posterior model I: Seal and reservoir likely thick}
		\begin{table}[h]
			\centering
			\begin{tabular}{lrr} 
				\toprule
				Model I - Likelihoods: layer thicknesses (normal distributions)\\  
				\midrule 
				Formation & $\mu$ [m] & $\sigma$ [m]\\ 
				\midrule 
				Sandstone 2 & 150 & 30 \\
				Shale (Seal) & 350 & 30\\ 
				Sandstone 1 (Reservoir) & 250 & 30 \\
				\bottomrule
			\end{tabular}
			\caption{Layer thickness likelihoods determined by normal distributions as used for posterior model I.}
			\label{tab:ML1_likelihoods}
		\end{table}
		For the simulation of this first posterior model, thickness likelihoods for the three central layers were included into the probabilistic model. These were defined in a way that reinforced the probabilities of the relevant layers to be significantly thick (see Table \ref{tab:ML1_likelihoods}). 
		\begin{figure}[p!]
			\centering
			\includegraphics[width=1\textwidth]{Figures/ML1}
			\caption{....}\label{fig:ML1}
		\end{figure}		
		Respective results are summarized in Figure \ref{fig:ML1}. Considering the changes in information entropy, it can be seen that the uncertainty about layer interface positions in $z$ was clearly reduced in the footwall. Information entropy decreased also in the middle section of the hanging wall, but remained high in upper and lower parts, presumably due to the remaining influence of the offset uncertainty.\\
		Regarding trap volume control (Figure \ref{fig:ML1} (c)), only spill point-related migration and cross-fault leakage due to juxtaposition with permeable layers below the seal in the hanging wall remain relevant in the posterior model. As no occurrences of leakage through overlying layers was observed, the two other mechanisms increased in frequency, while staying proportionally the same to one another. It can be presumed, that by introducing the respective likelihoods, a high thickness of the seal was ensured, as can also be recognized in Figure \ref{fig:ML1} (b). This not only made stratigraphic leakage in this model impossible, but also enforced a favorable $SSF$. A minor emergence of unrecognized control factors (label: "UNCLEAR") hints at a singular cases in which the model was possibly not correctly computable or the structural analysis failed for a different reason.\\
		The bulk that accounted for the positive mode in the prior $ROV$ distribution was raised and shifted laterally to higher values, while the probability of failure ($ROV = 0$) was diminished significantly. This can presumably be explained by the disappearing of leakage to overlying formations as a trap control mechanism, which was programmed to always lead to complete failure of the trap volume.\\
		As the probability of failure and thus the bimodality of the probability distribution disappeared, all Bayes actions were shifted to higher estimates, most significantly those of the two risk-averse individuals (see Figure \ref{fig:ML1} (e). There is thus clear convergence of the different points of minimum expected loss, which was also lowered overall. It is clear that the posterior state of knowledge, provided by the updated model, encourages even the most risk-averse decision-maker to expect recoverable oil volumes from 3.5 million m$^3$ upwards.

		\subsection{Posterior model II: Likely thin reservoir formation}%ML3
		For the following model, thickness likelihoods were defined in a way, that reinforced the probability of a very thick seal, but at the same time made restricted the reservoir formation to a likely significantly thinner reservoir (around 50 m) (see Table in Appendix). The results (see Appendix) are very similar to those of model I above. This can be explained by the influence of leak and spill point. As the shape of the general structure itself is not defined to be uncertain, the position of the anticlinal spill point relative to the fault top remains mostly unchanged, irrespective of layer thickness variations. Thus, reservoir thickness is a secondary factor to trap volume control. Given all other parameters are fixed, the maximum fill horizon is most likely the same for a 300 m as for a 50 m thick reservoir unit. The thickness of the reservoir only becomes respectively significant, if it thin enough to set the layer bottom above the leak and spill point depth in the trap section. Ultimately, the spill point appears to be the primariy limiting factor to maximum trap fill. It can furthermore be derived from this that the maximum trap volume capacity, as defined by the given structural features, is already represented in the $ROV$ probability distribution of the prior model. Examining this in Figure \ref{fig:ML1} (d), it seems that this overall maximum volume is found at around 5.7 millon m$3$. Higher values were not observed in any other model realization and are presumed to be unattainable due to the restriction given by the spill point.

		\subsection{Posterior model III}%ML2
		\begin{figure}[p!]
			\centering
			\includegraphics[width=1\textwidth]{Figures/ML2}
			\caption{....}\label{fig:ML2}
		\end{figure}
		Results from this third model show that in contrast to the reservoir thickness, seal thickness is a primary and decisive factor for trap volume. Using likelihoods which favor a thick reservoir, might only a thin seal of about 50 m thickness, leakage due to  
		- see ML2: seal thickness as decisive factor
			-> if seal thin and reservoir thick see the ratio of both!), higher likelihood of surpassing SSF
